ShrinkNets

### 2018-01-05 paper/paper.tex
Add ref to Gaussian process and some typos

When designing Neural Networks, finding the appropriate size (width and depth)
is key. In particular, these hyper parameters have a strong correlation with
over/underfitting \srm{give reference} \gl{I did some litterature review and
  actually this statement is quite controversial, should we rephrase ?}. We
have no reliable way to find them but decades of experimentation led to some
heuristics ~\cite{Bengio2012a} that try to prune that immense space of possible
network sizes and suggest range of values to explore. To select the best
candidates , researchers have used strategies such as random search \gl{Should
  we also move the references here if we remove the pargraph from the related
  work ?}, meta-gradient descent ~\cite{Pedregosa2016} and Parzen Estimators
~\cite{Bergstra2011a} to reduce find good parameters without exhaustively
exploring the entire hyper-parameter space. Although these strategies help with
finding a good set of hyper-parameters, they still require a compute-intensive
search of the space.

@@

This choice come from the Lasso loss ~\cite{Tibshirani1996} and we use it for the same reason:
it introduces sparsity. The bigger the $\lambda$ the more entries in $\theta$
are set to zer0, and since zero entries in $\theta$ correspond to dead neurons,
lambda effectively control the number of neurons/channels in the entire
network.
Next, we explain how to implement ShrinkNets efficiently.

\textbf{Software architecture\footnote{The code is available as Python/PyTorch
    library on \url{http://github.com/mitdbg/fastdeepnets} \gl{Should we rename
      the repository ?}}: }\textit{Filter Vectors} can easily be implemented in
a few lines of code in many existing deep learning frameworks. However, in
ShrinkNets, we assume that we start with obviously oversized networks. If
disabled neurons are not quickly removed, the overhead might cause the training
process to be significantly slower than classic neural networks. This is why we
want to support what we call garbage collection: removing the weights in the
layers that are responsible (or using) features that are disabled.  \par To be
able to catpure this relationship between layers, we agumented \textit{Pytorch}
~\cite{paszke2017automatic} (the framework we used as the
foundation of our implementation) with a graph structure very similar to the
one available in Keras ~\cite{chollet2015keras}.  In this graph, edges are
effectively event hubs responsible for propagating \textit{feature removal}
events to its endpoints. ShrinkNet layers are designed to emit and react to
these events but also propagate the event further if has an impact at the other
endpoint of the layer (input or output) \gl{What I mean here is: if the event
  comes from the output, it might be propagated to the inputs, and the other
  way around}.  \par This event-based implementation coordinated by edges makes
it very easy to integrate new layers in the library.  We even provide automatic
wrapping for layers from \textit{PyTorch} if they have no internal state. For
more complex ones, we provide utilitaries that
makes the implementation very concise.

@@

To demonstrate that the approach is viable, we will first show that Shrinking
Networks converge properly. For this experiment we trained a one hidden layer
neural network with one filter layer to control the number of hidden units. We
initialized the models with $10000$ neurons and trained them on \texttt{MNIST}
~\cite{Lecun1998} using different regularization factors ($\lambda$). We
summarized the results in \autoref{convergence_plot}. We can see on this plot
is that for a given $\lambda$ the number of hidden units seems to always
converge to some value. It has two implications: it seems that $\lambda$ is, as
we would think, a proxy of the network size (bigger $\lambda$ imply smaller
networks). Secondly, it indicates that the spikes we see in the regular spikes
we see in the loss that occur when neurons are disabled will eventually
disapear because the number of neurons reach a plateau. \gl{I feel we should
  give a conclusion for this paragraph but I am not sure what to say}
\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{convergence}
\caption{Evolution of the number of hidden units and loss over time on the \texttt{MNIST} dataset for different $\lambda$ values \label{convergence_plot}}
\end{center}
\end{figure}

>>>>

When designing Neural Networks, finding the appropriate size (width and depth)
is key. In particular, these hyper parameters have a strong correlation with
over/underfitting \srm{give reference} \gl{I did some litterature review and
  actually this statement is quite controversial, should we rephrase ?}. We
have no reliable way to find them but decades of experimentation led to some
heuristics ~\cite{Bengio2012a} that try to prune that immense space of possible
network sizes and suggest range of values to explore. To select the best
candidates , researchers have used strategies such as random search \gl{Should
  we also move the references here if we remove the pargraph from the related
  work ?}, meta-gradient descent ~\cite{Pedregosa2016} , gaussian processes
~\cite{Bergstra2011a}, and Parzen Estimators ~\cite{Bergstra2011a} to reduce
find good parameters without exhaustively exploring the entire hyper-parameter
space. Although these strategies help with finding a good set of
hyper-parameters, they still require a compute-intensive search of the space.

@@

This choice come from the Lasso loss ~\cite{Tibshirani1996} and we use it for the same reason:
it introduces sparsity. The bigger the $\lambda$ the more entries in $\theta$
are set to zero, and since zero entries in $\theta$ correspond to dead neurons,
lambda effectively control the number of neurons/channels in the entire
network.
Next, we explain how to implement ShrinkNets efficiently.

\textbf{Software architecture\footnote{The code is available as Python/PyTorch
    library on \url{http://github.com/mitdbg/fastdeepnets} \gl{Should we rename
      the repository ?}}: }\textit{Filter Vectors} can easily be implemented in
a few lines of code in many existing deep learning frameworks. However, in
ShrinkNets, we assume that we start with obviously oversized networks. If
disabled neurons are not quickly removed, the overhead might cause the training
process to be significantly slower than classic neural networks. This is why we
want to support what we call garbage collection: removing the weights in the
layers that are responsible (or using) features that are disabled.  \par To be
able to catpure this relationship between layers, we augmented \textit{Pytorch}
~\cite{paszke2017automatic} (the framework we used as the
foundation of our implementation) with a graph structure very similar to the
one available in Keras ~\cite{chollet2015keras}.  In this graph, edges are
effectively event hubs responsible for propagating \textit{feature removal}
events to its endpoints. ShrinkNet layers are designed to emit and react to
these events but also propagate the event further if has an impact at the other
endpoint of the layer (input or output) \gl{What I mean here is: if the event
  comes from the output, it might be propagated to the inputs, and the other
  way around}.  \par This event-based implementation coordinated by edges makes
it very easy to integrate new layers in the library.  We even provide automatic
wrapping for layers from \textit{PyTorch} if they have no internal state. For
more complex ones, we provide utilitaries that
makes the implementation very concise.

@@

To demonstrate that the approach is viable, we will first show that Shrinking
Networks converge properly. For this experiment we trained a one hidden layer
neural network with one filter layer to control the number of hidden units. We
initialized the models with $10000$ neurons and trained them on \texttt{MNIST}
~\cite{Lecun1998} using different regularization factors ($\lambda$). We
summarized the results in \autoref{convergence_plot}. We can see on this plot
is that for a given $\lambda$ the number of hidden units seems to always
converge to some value. It has two implications: it seems that $\lambda$ is, as
we would think, a proxy of the network size (bigger $\lambda$ imply smaller
networks). Secondly, it indicates that the  the regular spikes we see in the
loss function that occur when neurons are disabled will eventually disappear
because the number of neurons reach a plateau. \gl{I feel we should give a
  conclusion for this paragraph but I am not sure what to say}
\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{convergence}
\caption{Evolution of the number of hidden units and loss over time on the \texttt{MNIST} dataset for different $\lambda$ values \label{convergence_plot}}
\end{center}
\end{figure}
